Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A guide for Vietnamese and International Students

### 2023-06-12 phd-cs-us.tex
updates

@@

\begin{wrapfigure}{l}{0.47\textwidth}
    \vspace{-0.3in}
      \begin{center}
        \includegraphics[width=0.47\textwidth]{c5.png}
      \end{center}
    \vspace{-0.6in}
    \end{wrapfigure}
If you don't know that professor (e.g., first email contact), then use \textbf{Prof. Lastname} or \textbf{Dr. Lastname}. I've seen many international students write \textbf{Prof.} or \textbf{Dr.} \textbf{Firstname Lastname}.  Writing like that makes it like you copy and paste the names, so no need to do so,  just Prof. or Dr. Lastname.

>>>>

\subsection{How long does it take to complete the PhD program?}

\begin{wrapfigure}{r}{0.30\textwidth}
    \vspace{-0.2in}
      \begin{center}
        \includegraphics[width=0.30\textwidth]{c4a.png}
      \end{center}
    \vspace{-0.2in}
    \end{wrapfigure}
    Typically, 5-7 years for Ph.D. in CS at a US university.  The first 1.5--2 years you spend on coursework and research.  The next 2--3 years you focus on your research, forming dissertation topic, and getting results published.  The last 1-2 years you write and defend your dissertation and look for job. The figure on the right is from PhDComics and shows the "ambition" level of a PhD student over their study.

@@

\begin{wrapfigure}{l}{0.5\textwidth}
    \vspace{-0.4in}
      \begin{center}
        \includegraphics[width=0.5\textwidth]{c5.png}
      \end{center}
    \vspace{-0.9in}
    \end{wrapfigure}
If you don't know that professor (e.g., first email contact), then use \textbf{Prof. Lastname} or \textbf{Dr. Lastname}. I've seen many international students write \textbf{Prof.} or \textbf{Dr.} \textbf{Firstname Lastname}.  Writing like that makes it like you copy and paste the names, so no need to do so,  just Prof. or Dr. Lastname.
